---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Multiserver

<!-- badges: start -->
<!-- badges: end -->

The goal of Multiserver is to simulate how customers will go through a first come, first serve queuing system as long as “fate” has already decided when each customer will arrive and their service times.

## Installation

You can install the development version of Multiserver from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Het12345678/Multiserver")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Multiserver)
data(Bank)
with(bank, Multiserver(arrival_time, service_time, 4))
## basic example code
```

```{Marking Criteria for Exercise 3}
#' I have attempted all of these:
#' Had the correct R package structure; files were put in appropriate locations; the package can be installed [5 marks]
#' Had all the appropriate documentation for the package [4 marks]
#' Added the provided data set with proper documentation to the package [3 marks]
#' Implemented testthat correctly [4 marks]
#' Had used Git & Github correctly [2 marks]
#' Implemented tibble [2 marks]
```
